
%-
%- This file is part of the `robfrawley/latex-resume` project.
%-
%- (c) Rob M Frawley 2nd <rmf@src.run>
%-
%- For the full copyright and license information, please view the LICENSE.md
%- file that was distributed with this source code.
%-

%-
%- RENDER letterRecipient/TITLE/OPENING
%-
\letterTitle

%-
%- LETTER: START
%-
\begin{letterEnv}

    %
    % Section: ME
    %
    \letterSection{About}{Me}

    I have worked in Information Technology for over fifteen years, ever since freshman year of High School. The common thread
    throughout my years of experience is a willingness to peruse and overcome challenges, and a strong desire to continue
    to learn---both through self-education and my peers. Some of my most memorable days began with a newly identified
    unknown---days that centered around figuring a means to overcome a new obstacle, and ending with a appropriate resolution.
    I pride myself not based on my past resume experience, but instead on my continued interest in research, education, and
    continued growth.

    %
    % Section: YOU
    %
    \letterSection{Why}{RJ Metrics?}

    As a relatively new company, I am drawn to RJ Metrics due to the many milestones reached since its founding in 2008,
    including the execution of very respectable Seed, Series A, and Series B funding rounds, as well as demonstration of
    product value through the diverse customer-base. I am intrigued by the Cloud BI platform and sales strategy---allowing
    affordable plans for small-business clients, while remaining powerful enough to fulfill the needs and requirements of
    enterprise clients as well. Of particular interest is the impression of a ``start-up feel'' environment, while also
    offering the dependability of an established company as demononstated by the extensive publicly-advertised customer
    listings.

    %
    % Section: US
    %
    \letterSection{Why}{Me?}

    I believe RJ Metrics would be an excellent match for a number of reasons. I have extensive experience with infrastructure
    planning, deployment, and management; I managed the direction, planning, and implementation of hardware and software
    deployments at Westbrook High School and Scribe Inc. I have knowledge of OrangeFS, Ceph, and Hadoop distributed file
    systems, have managed deployments of MySQL, Percona Server, MariaDB, PostgresSQL, CouchDB, and Nginx, and have used a
    collection of *nix-based platforms, including custom bare-metal servers, Google Cloud Platform's Compute Engines, and
    Amazon Web Service's EC2s.

    I am also an experienced programmer. Having worked as the Lead Developer for my previous employer, as well as on an
    assortment of development teams throughout my career, I am comfortable working in both a leadership myPosition as well as
    a contributing member within a group of peers. Languages used in prior employs---as well as open-source projects
    I actively maintain---include PHP (version 5 and the newly released 7), Python, Ruby, C/C++, and JavaScript/HTML. Having
    gained a solid, abstract understanding of software development---utilizing established object-oriented patterns---I am
    able to easily and quickly establish myself with languages that I held no prior experience.

%-
%- LETTER: END
%-
\end{letterEnv}

%-
%- RENDER CLOSING
%-
\letterEnd

% EOF %
