%
% This file is part of the `latex-cv` project.
%
% (c) Rob M Frawley 2nd <rmf@src.run>
% (c) Claud D. Park <posquit0.bj@gmail.com>
%
% For the full copyright and license information, please view the LICENSE.md
% file that was distributed with this source code.
% Class license:
% LPPL v1.3c (http://www.latex-project.org/lppl)
%

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%   LETTER CONTENT
%-------------------------------------------------------------------------------

\begin{cvletter}

\lettersection{About}{Me}
I have worked in Information Technology for over fifteen years, ever since freshman year of High School. The common thread
throughout my years of experience is a willingness to peruse and overcome challenges, and a strong desire to continue
to learn---both through self-education and my peers. Some of my most memorable days began with a newly identified
unknown---days that centered around figuring a means to overcome a new obstacle, and ending with a appropriate resolution.
I pride myself not based on my past resume experience, but instead on my continued interest in research, education, and
continued growth.

\lettersection{Why}{RJ Metrics?}
As a relatively new company, I am drawn to RJ Metrics due to the many milestones reached since its founding in 2008,
including the execution of very respectable Seed, Series A, and Series B funding rounds, as well as demonstration of
product value through the diverse customer-base. I am intrigued by the Cloud BI platform and sales strategy---allowing
affordable plans for small-business clients, while remaining powerful enough to fulfill the needs and requirements of
enterprise clients as well. Of particular interest is the impression of a ``start-up feel'' environment, while also
offering the dependability of an established company (established through the extensive publicly-advertised customer
listing).

\lettersection{Why}{Me?}
I believe RJ Metrics would be an excellent match for a number of reasons. I have extensive experience with infrastructure
planning, deployment, and management; I managed the direction, planning, and implementation of hardware and software
deployments at Westbrook High School and Scribe Inc. I have knowledge of OrangeFS, Ceph, and Hadoop distributed file
systems, have managed deployments of MySQL, Percona Server, MariaDB, PostgresSQL, CouchDB, and Nginx, and have used a
collection of *nix-based platforms, including custom bare-metal servers, Google Cloud Platform's Compute Engines, and
Amazon Web Service's EC2s.

I am also an experienced programmer. Having worked as the Lead Developer for my previous employer, as well as on an
assortment of development teams throughout my career, I am comfortable working in both a leadership position as well as
a contributing member within a group of peers. Languages used in prior employs---as well as open-source projects
I actively maintain---include PHP (version 5 and the newly released 7), Python, Ruby, C/C++, and JavaScript/HTML. Having
gained a solid, abstract understanding of software development---utilizing established object-oriented patterns---I am
able to easily and quickly establish myself with languages that I held no prior experience.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

% EOF %
